Chemically Selective Transport in a Cross-linked H\textsubscript{II} Phase Lyotropic Liquid Crystal Membrane

### 2019-04-16 Ben_Manuscripts/transport/Draft.tex
New figures from new plotting scripts

\usepackage{graphicx}
\usepackage{wrapfig}
\usepackage{subcaption}
\usepackage{amsmath} % or simply amstext
\usepackage{amssymb}
\usepackage{siunitx}
\usepackage{booktabs}
\usepackage[export]{adjustbox}
\newcommand{\angstrom}{\textup{\AA}}
\newcommand{\colormap}{jet}  % colorbar to use
\usepackage{cleveref}
\usepackage{booktabs}
\usepackage{gensymb}
\usepackage{float}
\usepackage{xr}
\usepackage{tcolorbox}
\usepackage{multicol}

@@

%MRS2: ``dependent -> selective?'' 
\title{Chemically Dependent Transport in a Cross-linked H\textsubscript{II} Phase Lyotropic Liquid Crystal Membrane}
\author{Benjamin J. Coscia}
\affiliation{Department of Chemical and Biological Engineering, University of Colorado Boulder, Boulder, CO 80309, USA}
\author{Michael R. Shirts}
\email{michael.shirts@colorado.edu}
\affiliation{Department of Chemical and Biological Engineering, University of Colorado Boulder, Boulder, CO 80309, USA}

%MRS2: I think it would be useful to have a picture of the pores to
% allow people to visualize what was going on.  ToC might be good, 
% but I think that as people read, they need to see the 3D picture as well to think through things.

@@

  The uniform size and complex chemical topology of the pores that 
  constitute cross-linked inverted hexagonal (H\textsubscript{II})
  phase lyotropic liquid crystal (LLC) membranes make them promising
  for selective separations. In this work, we observe transport
  of water, sodium ions and 20 small polar solutes within the pores 
  of an LLC membrane using atomistic molecular simulations. We 
  %MRS2: 
  find
  %found
  %MRS2: ``transport rate -> transport''
  that the transport rate of a species is dependent not only on 
  molecular size, but on chemical functionality as well. The 
  membrane's inhomogeneous composition gives rise to radially dependent
  transport mechanisms with respect to the pore centers. In general, we 
  observed that all solutes perform intermittent hops between lengthy
  periods of entrapment. Three different trapping mechanisms are 
  responsible for this behavior. First, solutes that drift
  out of the pore can become entangled among the dense monomer
  tails. Second, solutes can donate hydrogen bonds to the monomer
  head groups. Third, solutes can coordinate with sodium counter ions.
  The degree to which a solute is affected by each mechanism is 
  dependent on the chemical functionality of the solute. Using the
  insights developed in this study, we can begin to think about 
  how to redesign existing LLC membranes in order to perform 
  solute-specific separations.

@@

  Membranes capable of separating nm-sized solutes with high selectivity 
  and permeability are highly desirable for a number of applications. For 
  example, separation of salt from seawater or other briny sources can 
  yield potable drinking water.~\cite{fritzmann_state---art_2007} Removal
  of organic micropollutants, such as personal care products, pesticides
  and pharmaceuticals, from surface and groundwaters, can have large benefits
  for public health.~\cite{schwarzenbach_challenge_2006} Finally,
  one can purify and recover dissolved species present in complex
  hydraulic fracturing flowback water waste streams which would help mitigate
  the effects of deep well injection and generate value.~\cite{dischinger_application_2017} 
  %BJC: could make last point more general
  %MRS2: ``generate value'' is pretty vague, yeah.

%  All of these separations are possible with current commercial membrane
%  separation techniques but they are too energy intensive to be worth the 
%  capital investment needed to start the processes  
% MRS2: maybe ``are possible'' -> ``are possible in part''?  Otherwise, it logically follows that they shouldn't have major drawbacks.
  All of these separations are possible with current commercial membrane
  separation techniques but suffer from serious drawbacks. Currently, reverse 
  osmosis (RO) and nanofiltration (NF) dominate commercial membrane separations
  of small molecules.~\cite{warsinger_review_2018} RO membranes are typically
  dense polymer matrices that separate solutes based on differences in their
  solubility and permeability in the membrane material.~\cite{fritzmann_state---art_2007}
  Although they can perform highly selective separations, high feed pressures,
  and thus large amounts of energy, are necessary in order to generate a 
  useful permeate flux.~\cite{van_der_bruggen_review_2003} NF membranes have 
  well-defined nm-sized pores which can give the same permeate flux as RO
  with lower applied pressure.~\cite{hilal_comprehensive_2004} However, the 
  pores are not uniform in size, limiting selectivity.~\cite{werber_materials_2016}.
%  Therefore, multiple membrane passes may be necessary in order to achieve 
%  high selectivity.

@@

  While H\textsubscript{II} membranes have been synthesized and characterized
  in a lab setting, there is a limit to the level of detail that can be obtained 
  from experiment. The separation performance of these membranes has been 
  primarily characterized with size-exclusion experiments which emphasizes 
  selectivity based on the ability to enter a given pore.~\cite{zhou_supported_2005}
  While size-exclusion is a useful separation, it cannot reliably purify a 
  solution where the solute size is on the same order as water. Therefore, it is
  important to take advantage of material properties other than pore size. 
  %MRS2: is ``complexity'' the right word? Can we be more specific?
  Unfortunately, the complexity of LLC membranes has obscured the interpretation
  of experimental transport studies.~\cite{dischinger_effect_2017}  % BJC: ref to Sarah?

  %MRS2: odd to have a one sentence paragraph?  MAyber just join with the next paragraph.
  Molecular dynamics (MD) simulations can give us mechanistic insights with 
  atomistic resolution so that we can directly observe small solute transport
  within LLC membrane nanopores and intelligently design new membranes for 
  solute-specific separations.

  In our previous work, we used MD simulations to determine the most likely 
  structure of the hexagonal phase formed by the monomer Na-GA3C11, expanding 
  upon the most recent experimental characterization.~\cite{coscia_understanding_2018,feng_thin_2016}
  We developed techniques for equilibrating the hexagonal phase formed by neat 
  monomer as well as with varying amounts of water in the pores.

  %BJC: is a figure with all the solutes necessary? would take up a lot of space. maybe supporting
  In this work, we have studied the transport mechanisms exhibited by 20 
  uncharged polar solutes with varying size, chemical functionality and hydrophilic 
  character. We have listed the solutes studied along with the abbreviations that
  we will use in the charts for the remainder of this paper in Table~\ref{table:abbreviations}.
%  Many of the separations we are interested in involve polar organic 
%  compounds.

  % BJC: not sure if I should just leave formatting to the journal. Thought tcolorbox was neat though
  % I can easily change these abbreviations and have them applied to all the figures. I haven't given
  % them much thought. Just used their residue names
  \begin{table}
  \centering
  \begin{tcolorbox}[%
  	colframe=blue,
  	title=\centering \textbf{Solute Names and Their Abbreviations},
  	width=0.7\textwidth,
  	box align=center,
  	halign=center,
  	valign=center,
  	fontupper=\linespread{1}\selectfont]

  \begin{multicols}{2}

  \textbf{Name} \\
  Acetic Acid \\
  Acetamide \\
  Acetone \\
  Butanol \\
  Dimethyl Formamide \\
  2,3-Dimercapto-1-propanol \\
  Dimethyl Sulfoxide \\
  Ethyl Acetate \\ 
  Ethanol \\
  Ethylene Glycol \\
  Glycerol \\
  Methanol \\ 
  Propylene Carbonate \\
  Propylene Glycol \\
  Propanol \\
  Ribose \\
  Mercaptoethanol \\
  Tetrose \\
  Tetrahydrofuran \\
  Urea \\
  \columnbreak

  \textbf{Abbrevation} \\
  ACH \\  
  ACN \\
  ATO \\
  BUT \\
  DMF \\
  DMP \\
  DMSO \\
  EAC \\ 
  ETH \\
  GCL \\
  GLY \\
  MET \\
  PCB \\ 
  PG \\
  PR \\
  RIB \\ 
  SOH \\ 
  TET \\
  THF \\ 
  URE \\

  \end{multicols}

  %MRS2: can you put molecules in the table as well? I think it would be better for reference. Some of the larger ones may have small molecules.  You can potentially partially stagger them horizontally so the size can be OK? 
  \end{tcolorbox}
  \caption{}\label{table:abbreviations}
  \end{table}

  %MRS2: generally, use present tense for what is being done in the paper, not future tense; 
  %the paper is completely written, later sections are not being written in the future. 
  %MRS2: descriptions of experiements can be in the past.   
  %First, we will comment on the membrane's structure. 
  We first address the structure of the pores formed in the membrane.
  Previously, we have
  studied dry membrane systems and some systems with low water content. 
  We will observe how the radial density of monomer components and water 
  change within the oore based on membrane water content.

  % BJC: I don't really explicity comment on the partitioning of solutes
  % out of the pore. Maybe I can add some sort of chart. Need to think more.
  % MRS2: it should be mentioned somewhere, probably worth a paragraph or so.  
  % If WATER is much slower outside of the pores, everything else will be slow as well, so we can
  % justify transport there not being interesting
  %Then we will present 
  We then present
  our efforts to understand how small molecules, 
  including water, partition within the pores. From a macroscopic perspective,
  it is straightforward to hypothesize that the water and polar solutes spend
  their time exclusively in the tube-like hydrophilic pore region. Our
  previous work showed that there is a gradual compositional transition from
  the hydrophilic to the hydrophobic region which means that solutes may not
  necessarily stay confined to the centers of the pores or even within the 
  pore region. 
  %MRS2:
  %We will 
  We then study the gradient in composition of solutes and 
  water and any resultant influence it might have on mechanistic properties.
  %MRS2: tweak
  %Finally, and for the bulk of this work, we will 
  For the remainder of the paper, we 
  present our observations 
  and explanations of the observed transport mechanisms exhibited by water
  and solutes. Given that the pores will restrict motion of the solutes, we
  anticipate that transport will be hindered in some way.

  %MRS2: next line is a statement about what we want to do, not what we did?
  %We want to understand
  We investigate
  the differences in solute motion, specifically its mean squared displacement 
  (MSD), based on a solute's size, shape and chemical functionality. We will 
  study the interactions between solutes, the membrane, and water in order to
  determine which mechanism or mechanisms dominate.

@@

@@

>>>>

\usepackage{graphicx}
\usepackage{wrapfig}
\usepackage{subcaption}
\usepackage{amsmath} % or simply amstext
\usepackage{amssymb}
\usepackage{array}
\usepackage{siunitx}
\usepackage{booktabs}
\usepackage[export]{adjustbox}
\newcommand{\angstrom}{\textup{\AA}}
\newcommand{\colormap}{jet}  % colorbar to use
\usepackage{cleveref}
\usepackage{booktabs}
\usepackage{gensymb}
\usepackage{float}
\usepackage{xr}
\usepackage{tcolorbox}
\usepackage{multicol}

@@

\title{Chemically Selective Transport in a Cross-linked H\textsubscript{II} Phase Lyotropic Liquid Crystal Membrane}
\author{Benjamin J. Coscia}
\affiliation{Department of Chemical and Biological Engineering, University of Colorado Boulder, Boulder, CO 80309, USA}
\author{Michael R. Shirts}
\email{michael.shirts@colorado.edu}
\affiliation{Department of Chemical and Biological Engineering, University of Colorado Boulder, Boulder, CO 80309, USA}

% MRS2: I think it would be useful to have a picture of the pores to 
% allow people to visualize what was going on. ToC might be good, 
% but I think that as people read, they need to see the 3D picture 
% as well to think through things.

@@

  The uniform size and complex chemical topology of the pores that 
  constitute cross-linked inverted hexagonal (H\textsubscript{II})
  phase lyotropic liquid crystal (LLC) membranes make them promising
  for selective separations. In this work, we observe transport
  of water, sodium ions and 20 small polar solutes within the pores 
  of an LLC membrane using atomistic molecular simulations. We 
  find that the transport of a species is dependent not only on 
  molecular size, but on chemical functionality as well. The 
  membrane's inhomogeneous composition gives rise to radially dependent
  transport mechanisms with respect to the pore centers. In general, we 
  observed that all solutes perform intermittent hops between lengthy
  periods of entrapment. Three different trapping mechanisms are 
  responsible for this behavior. First, solutes that drift
  out of the pore can become entangled among the dense monomer
  tails. Second, solutes can donate hydrogen bonds to the monomer
  head groups. Third, solutes can coordinate with sodium counter ions.
  The degree to which a solute is affected by each mechanism is 
  dependent on the chemical functionality of the solute. Using the
  insights developed in this study, we can begin to think about 
  how to redesign existing LLC membranes in order to perform 
  solute-specific separations.

@@

  Membranes capable of separating nm-sized solutes with high selectivity 
  and permeability are highly desirable for a number of applications. For 
  example, separation of salt from seawater or other briny sources can 
  yield potable drinking water.~\cite{fritzmann_state---art_2007} Removal
  of organic micropollutants, such as personal care products, pesticides
  and pharmaceuticals, from surface and groundwaters, can have large benefits
  for public health.~\cite{schwarzenbach_challenge_2006} Finally,
  one can purify and recover dissolved species present in complex
  hydraulic fracturing flowback water waste streams which would help mitigate
  the effects of deep well injection and can be sold for profit.~\cite{dischinger_application_2017}

  All of these separations are possible in part with current commercial membrane
  separation techniques but suffer from serious drawbacks. Currently, reverse 
  osmosis (RO) and nanofiltration (NF) dominate commercial membrane separations
  of small molecules.~\cite{warsinger_review_2018} RO membranes are typically
  dense polymer matrices that separate solutes based on differences in their
  solubility and permeability in the membrane material.~\cite{fritzmann_state---art_2007}
  Although they can perform highly selective separations, high feed pressures,
  and thus large amounts of energy, are necessary in order to generate a 
  useful permeate flux.~\cite{van_der_bruggen_review_2003} NF membranes have 
  well-defined nm-sized pores which can give the same permeate flux as RO
  with lower applied pressure.~\cite{hilal_comprehensive_2004} However, the 
  pores are not uniform in size, limiting selectivity.~\cite{werber_materials_2016}.
%  Therefore, multiple membrane passes may be necessary in order to achieve 
%  high selectivity.

@@

  While H\textsubscript{II} membranes have been synthesized and characterized
  in a lab setting, there is a limit to the level of detail that can be obtained 
  from experiment. The separation performance of these membranes has been 
  primarily characterized with size-exclusion experiments which emphasizes 
  selectivity based on the ability to enter a given pore.~\cite{zhou_supported_2005}
  While size-exclusion is a useful separation, it cannot reliably purify a 
  solution where the solute size is on the same order as water. Therefore, it is
  important to take advantage of material properties other than pore size. 
  Unfortunately, interactions between solutes and pore moieties have yielded
  unclear trends in experimental transport studies.~\cite{dischinger_effect_2017}

  Molecular dynamics (MD) simulations can give us mechanistic insights with 
  atomistic resolution so that we can directly observe small solute transport
  within LLC membrane nanopores and intelligently design new membranes for 
  solute-specific separations. In our previous work, we used MD simulations to 
  determine the most likely structure of the hexagonal phase formed by the monomer
  Na-GA3C11, expanding upon the most recent experimental characterization.~\cite{coscia_understanding_2018,feng_thin_2016}
  We developed techniques for equilibrating the hexagonal phase formed by neat 
  monomer as well as with varying amounts of water in the pores.

  %BJC: is a figure with all the solutes necessary? would take up a lot of space. maybe supporting
  In this work, we have studied the transport mechanisms exhibited by 20 
  uncharged polar solutes with varying size, chemical functionality and hydrophilic 
  character. We have listed the solutes studied along with the abbreviations that
  we will use in the charts for the remainder of this paper in Table~\ref{table:abbreviations}.
  Note that, in order to avoid studying charge species, we have only studied
  %BJC: citations for pKa's
  acetic acid in its protonated form. The pKa of gallic acid is 4.40 while the
  pKa of acetic acid is 4.75. Assuming that the pKa of gallic acid is similar 
  to NaGA3C11, it is possible for our sodium salted monomer to exist at the 
  same time as protonated acetic acid.

%  % BJC: not sure if I should just leave formatting to the journal. Thought tcolorbox was neat though
%  % I can easily change these abbreviations and have them applied to all the figures. I haven't given
%  % them much thought. Just used their residue names
%  \begin{table}
%  \centering
%  \begin{tcolorbox}[%
%  	colframe=blue,
%  	title=\centering \textbf{Solute Names and Their Abbreviations},
%  	width=0.7\textwidth,
%  	box align=center,
%  	halign=center,
%  	valign=center,
%  	fontupper=\linespread{1}\selectfont]
%
%  \begin{multicols}{2}
%
%  \textbf{Name} \\
%  Acetic Acid \\
%  Acetamide \\
%  Acetone \\
%  Butanol \\
%  Dimethyl Formamide \\
%  2,3-Dimercapto-1-propanol \\
%  Dimethyl Sulfoxide \\
%  Ethyl Acetate \\ 
%  Ethanol \\
%  Ethylene Glycol \\
%  Glycerol \\
%  Methanol \\ 
%  Propylene Carbonate \\
%  Propylene Glycol \\
%  Propanol \\
%  Ribose \\
%  Mercaptoethanol \\
%  Tetrose \\
%  Tetrahydrofuran \\
%  Urea \\
%  \columnbreak
%
%  \textbf{Abbrevation} \\
%  AcOH \\  % Acetic acid
%  AcN \\  % Acetamide
%  ACE \\  % Acetone
%  BtOH \\  % Butanol
%  DMF \\  % Dimethyl Formamide
%  DMP \\  % 2,3-Dimercapto-1-propanol
%  DMSO \\  % Dimethyl sulfoxide
%  ETAC \\  % Ethyl Acetate
%  EtOH \\  % ethanol
%  EG \\  % ethylene glycol
%  GLY \\  % glycerol
%  MeOH \\  % methanol
%  PC \\ % propylene carbonate
%  PG \\  % propylene glycol
%  PrOH \\  % propanol
%  RIB \\ 
%  ME \\ % mercaptoethanol
%  TET \\
%  THF \\ 
%  URE \\
%  
%  \end{multicols}
%  
%  %MRS2: can you put molecules in the table as well? I think it would be better for reference. Some of the larger ones may have small molecules. You can potentially partially stagger them horizontally so the size can be OK? 
%  \end{tcolorbox}
%  \caption{}\label{table:abbreviations}
%  \end{table}

  \begin{table}[h!]
  \centering
%  \begin{minipage}{.4\textwidth}
%  \tiny
  \begin{tabular}{ |lcclcc| }
    \hline
    Name & Abbreviation & Structure & Name & Abbreviation & Structure \\ \hline

	\color{blue}{Methanol} & \color{blue}{MeOH} &     
    \begin{minipage}{.1\textwidth}
    \includegraphics[width=\linewidth]{structures/methanol.png}
    \end{minipage} \\

   	\color{blue}{Ethanol} & \color{blue}{EtOH} &     
    \begin{minipage}{.1\textwidth}
    \includegraphics[width=\linewidth]{structures/methanol.png}
    \end{minipage} \\

  	\color{blue}{Propanol} & \color{blue}{PrOH} &     
    \begin{minipage}{.1\textwidth}
    \includegraphics[width=\linewidth]{structures/methanol.png}
    \end{minipage} \\

    \color{blue}{Butanol} & \color{blue}{BtOH} &     
    \begin{minipage}{.1\textwidth}
    \includegraphics[width=\linewidth]{structures/methanol.png}
    \end{minipage} \\

    \color{red}{Ethylene Glycol} & \color{red}{EG} &     
    \begin{minipage}{.1\textwidth}
    \includegraphics[width=\linewidth]{structures/methanol.png}
    \end{minipage} \\

    \color{red}{Propylene Glycol} & \color{red}{PG} &     
    \begin{minipage}{.1\textwidth}
    \includegraphics[width=\linewidth]{structures/methanol.png}
    \end{minipage} \\

    \color{red}{Glycerol} & \color{red}{GLY} &     
    \begin{minipage}{.1\textwidth}
    \includegraphics[width=\linewidth]{structures/methanol.png}
    \end{minipage} \\

    \color{red}{Tetrose} & \color{red}{TET} &     
    \begin{minipage}{.1\textwidth}
    \includegraphics[width=\linewidth]{structures/methanol.png}
    \end{minipage} \\

    \color{red}{Ribose} & \color{red}{RIB} &     
    \begin{minipage}{.1\textwidth}
    \includegraphics[width=\linewidth]{structures/methanol.png}
    \end{minipage} \\

    \color{green!40!olive}{Acetic Acid} & \color{green!40!olive}{AcOH} &     
    \begin{minipage}{.1\textwidth}
    \includegraphics[width=\linewidth]{structures/methanol.png}
    \end{minipage} \\
%    \hline
%    \end{tabular}
%    \end{minipage}%
%    
%    \begin{minipage}{.2\linewidth}
%    \tiny
%    \begin{tabular}{ | l c c | }
%    \hline
%    Name & Abbreviation & Structure \\ \hline
    \color{green!40!olive}{Urea} & \color{green!40!olive}{URE} &     
    \begin{minipage}{.1\textwidth}
    \includegraphics[width=\linewidth]{structures/methanol.png}
    \end{minipage} \\

    \color{green!40!olive}{Acetamide} & \color{green!40!olive}{AcN} &     
    \begin{minipage}{.1\textwidth}
    \includegraphics[width=\linewidth]{structures/methanol.png}
    \end{minipage} \\

    \color{green!40!olive}{Acetone} & \color{green!40!olive}{ACE} &     
    \begin{minipage}{.1\textwidth}
    \includegraphics[width=\linewidth]{structures/methanol.png}
    \end{minipage} \\

    \color{orange}{Mercaptoethanol} & \color{orange}{ME} &     
    \begin{minipage}{.1\textwidth}
    \includegraphics[width=\linewidth]{structures/methanol.png}
    \end{minipage} \\

    \color{orange}{Dimethyl Sulfoxide} & \color{orange}{DMSO} &     
    \begin{minipage}{.1\textwidth}
    \includegraphics[width=\linewidth]{structures/methanol.png}
    \end{minipage} \\

    \color{orange}{2,3-Dimercapto-1-propanol} & \color{orange}{DMP} &     
    \begin{minipage}{.1\textwidth}
    \includegraphics[width=\linewidth]{structures/methanol.png}
    \end{minipage} \\

    \color{yellow!70!orange}{Tetrahydrofuran} & \color{yellow!70!orange}{THF} &     
    \begin{minipage}{.1\textwidth}
    \includegraphics[width=\linewidth]{structures/methanol.png}
    \end{minipage} \\

    \color{yellow!70!orange}{Dimethylformamide} & \color{yellow!70!orange}{DMF} &     
    \begin{minipage}{.1\textwidth}
    \includegraphics[width=\linewidth]{structures/methanol.png}
    \end{minipage} \\

    \color{yellow!70!orange}{Propylene Carbonate} & \color{yellow!70!orange}{PC} &     
    \begin{minipage}{.1\textwidth}
    \includegraphics[width=\linewidth]{structures/methanol.png}
    \end{minipage} \\

    \color{yellow!70!orange}{Ethyl Acetate} & \color{yellow!70!orange}{EAC} &     
    \begin{minipage}{.1\textwidth}
    \includegraphics[width=\linewidth]{structures/methanol.png}
    \end{minipage} \\
    \hline
  \end{tabular}
%  \end{minipage}
  \caption{}\label{table:abbreviations}
  \end{table}

  %MRS2: generally, use present tense for what is being done in the paper, not future tense; 
  %the paper is completely written, later sections are not being written in the future. 
  %MRS2: descriptions of experiements can be in the past.

  We first address the structure of the pores formed in the membrane.
  Previously, we have studied dry membrane systems and some systems with 
  low water content. We will observe how the radial density of monomer 
  components and water change within the pore based on membrane water content.

  We then present our efforts to understand how small molecules, 
  including water, partition within the pores. From a macroscopic perspective,
  it is straightforward to hypothesize that the water and polar solutes spend
  their time exclusively in the tube-like hydrophilic pore region. Our
  previous work showed that there is a gradual compositional transition from
  the hydrophilic to the hydrophobic region which means that solutes may not
  necessarily stay confined to the centers of the pores or even within the 
  pore region. We then study the gradient in composition of solutes and 
  water and any resultant influence it might have on mechanistic properties.

  For the remainder of the paper, we present our observations 
  and explanations of the observed transport mechanisms exhibited by water
  and solutes. Given that the pores will restrict motion of the solutes, we
  anticipate that transport will be hindered in some way.

  We investigate the differences in solute motion, specifically its mean 
  squared displacement (MSD), based on a solute's size, shape and chemical
  functionality. We will study the interactions between solutes, the membrane,
  and water in order to determine which mechanism or mechanisms dominate.

@@

  In the 10 wt\% water system, water molecules that spend the majority of 
  their time in the distal tail region move significantly slower than those
  confined to the pore region. In Figure~\ref{fig:water_msd_comparison}, we 
  constructed the MSD curves based on water molecules that spent > 95\% of their
  time in the pore region. If we instead restrict our calculation to water molecules
  that spend > 95\% of their time in the distal tail region, the MSD of distal tail
  water decreases 8-fold compared to pore water.

  % Changing pore radius does not change conclusion here.
  In the 5 wt\% water system, water molecules that spend the majority of their 
  time in the distal tail region have MSDs comparable to those of water molecules
  which stay in the pore region. The MSD of distal tail water molecules is 1.71 nm$^2$,
  which is actually higher than that of pore water. This anomaly is likely a consequence
  of low density in the distal tails as well as structuring of water molecules. 
  Water molecules are less likely to interact via hydrogen bonding while in the distal 
  tail region since they are interspersed between chains, while they are in close
  proximity in the pores.
  % BJC: quantify this. Number of hbonds per frame.

@@

  % BJC: Clauset has an easily understood test for exponential versus power law. Would take
  % me maybe half a day to implement and generate results. Not sure if necessary though since
  % I'm just going to say that I don't know what distribution it is and we are going to
  % use a percentile.
  Hydrogen bond lifetimes appear to be distributed according to a power law or an
  exponential function. A number of researchers provide evidence that supports a 
  power law distribution~\cite{starr_fast_1999,martiniano_insights_2013}. However, these
  studies were done on extremely short timescales relative to ours, outputting positions
  every timestep. Voloshin et al. studied hydrogen bonding on multiple timescales and 
  observed exponential behavior on the longest timescales~\cite{voloshin_hydrogen_2009}. 
  We do not collect data frequently enough to provide a sufficient answer to this 
  question so we instead report the 95\textsuperscript{th} percentile of hydrogen bond dwell times.
  This places emphasis on solutes with long dwell times.
